---
title: "tpt_final"
author: "Brook Frye"
date: "3/10/2020"
output: html_document
---

```{r echo=FALSE, warning=FALSE, message=FALSE}
# read in the data
library(data.table)
library(ggplot2)
library(leaflet)
library(sf)
library(councildown)
library(survival)
library(survminer)
library(stringr)
library(data.table)
library(readxl)
library(knitr)
library(readr)
library(data.table)
library(httr)
source("code/get_lat_lon.R")
source("code/lien_clean_agg.R")

# add to this 
# data sources: https://data.cityofnewyork.us/City-Government/Property-Exemption-Detail/muvi-b6kx

# read in aep data, check it out, make sure that it's good 
hmcv <- fread("data/hmcv.csv")
aep <- fread("https://data.cityofnewyork.us/resource/hcir-3275.csv?$limit=99999")
tpt <- readxl::read_excel("~/Desktop/housing_builds/HPD Lien/AEP/data/tpt.xlsx")
tpt_admin <- read_excel("~/Desktop/housing_builds/HPD Lien/AEP/data/admin_tpt.xlsx")
setDT(tpt_admin); setDT(tpt)

names(tpt_admin) <- as.character(tpt_admin[1, ])
tpt_admin <- tpt_admin[-1, ] 

bc <- hmcv[class %in% c("B", "C"), ]

# subset to the open violations/clean/make vars
bc <- bc[violationstatus %in% "Open", ]
bc[, novissueddate := as.Date(novissueddate)]
bc[, .N, by = c("bbl")][order(N, decreasing = TRUE)]

bc[, add := paste(housenumber, streetname)]
bc[,  address := paste(housenumber, streetname, zip)]
bc[, address_apt:= paste(apartment, address, sep = " ")]
bc[, bbl := as.character(bbl)]
c <- bc[class %in% "C", ]


# aep clean 
aep[, aep_start_date := as.Date(aep_start_date)]
aep[, discharge_date := as.Date(discharge_date)]
aep[, address := paste(phn, street_address, postcode)]
aep[ , time_in_aep := discharge_date - aep_start_date, by = aep_round]
aep[, days_in_aep := as.numeric(time_in_aep)]
aep[total_units > 5 & total_units <= 14, units_char:= "Btwn 6 and 14" ]
aep[total_units<= 5, units_char:= "5 or less" ]
aep[total_units > 14, units_char:= "15 or more" ]
aep[, units_char:= factor(units_char, levels = c("5 or less", 
                                                    "Btwn 6 and 14", 
                                                    "15 or more"))]


aep[, num_aep := .N,  by = "address"]
aep[, bbl := as.character(bbl)]

aep_bc <- merge(aep, bc, by = c("address", "bbl"))
aep_bc <- aep_bc[, .(address, aep_start_date, discharge_date, latitude = latitude.x,
                     longitude = longitude.x, violationid, currentstatus, 
                     total_units, num_aep, novissueddate, violationstatus,
                     aep_round, units_char, of_b_c_violations_at_start)]

aep_bc <- aep_bc[novissueddate > aep_start_date, ]
aep_bc[, n_vios:=length(unique(violationid)), by = "address"]

rnd_12 <- aep[aep_round %in% "Aep Round 12", .N, by = "units_char"]
rnd_12[units_char %in% "10 or less", ]



tpt[Borough %in% "QUEENS", boro := 4]
tpt[Borough %in% "BROOKLYN", boro := 3]
tpt[Borough %in% "MANHATTAN", boro := 1]
tpt[Borough %in% "BRONX", boro := 2]

# let's pad the strings 
tpt[, block := str_pad(Block, 5, "left", pad = 0)]
tpt[, lot := str_pad(Lot, 4, "left", pad = 0)]

# make bbl 
tpt[, bbl := paste(boro, block, lot, sep = "")]
tax_exem <- fread("https://data.cityofnewyork.us/resource/muvi-b6kx.csv?$limit=9999999")
tax_exem[, bbl := parid]

pluto <- fread("data/pluto_19v1.csv")
pluto[, bbl := as.character(bbl)]

# what do we need from pluto 
pluto_sub <- pluto[, .(bbl, unitsres)]
# pluto_sub[, address := paste(address, zipcode, sep=" ")]

 # maybe get bbl 
# bc[grep("Davidson", address, ignore.case = TRUE), unique(address)]

# subset to 5129 
damp <- tax_exem[exmp_code %in% "5129", ] # if we are interested in the number of 
```


#### what is the distribution of open b & c violations for properties that have been selected tpt (admin file)
```{r echo=FALSE, warning=FALSE, message=FALSE}

```

#### what is the distribution of (open) b & c violations for properties that have gone through tpt (tolani file)
```{r echo=FALSE, warning=FALSE, message=FALSE}

```


#### what is the distribution of open b&c violations for the entire city, normalized by units, broken up by size  
```{r echo=FALSE}
# bring in pluto data to get units
bc_pluto <- merge(bc, pluto_sub, by = "bbl")
bc_pluto[, n_vios := length(unique(violationid)), by = "address"]

bc_pluto <- bc_pluto[unitsres>=3, ]

setnames(bc_pluto, "unitsres", "total_units")
# let's break up by size of building

bc_pluto[total_units > 5 & total_units <= 14, units_char:= "Btwn 6 and 14" ]
bc_pluto[total_units<= 5, units_char:= "5 or less" ]
bc_pluto[total_units > 14, units_char:= "15 or more" ]
bc_pluto[, units_char:= factor(units_char, levels = c("5 or less", 
                                                    "Btwn 6 and 14", 
                                                    "15 or more"))]



bc_pluto[, n_vios_norm := n_vios/total_units]

dt <- unique(bc_pluto[, .(address, n_vios_norm, n_vios, units_char, total_units)])

dt <- unique(dt)
ggplot(dt, aes(x=n_vios)) + geom_histogram()
summary(dt$n_vios)

ggplot(dt[units_char %in% "5 or less", ], aes(x=n_vios_norm)) + geom_histogram() + ggtitle("Norm Viols for 5 or less")
dt[units_char %in% "5 or less", summary(n_vios_norm)]

ggplot(dt[units_char %in% "Btwn 6 and 14", ], aes(x=n_vios_norm)) + geom_histogram() + ggtitle("Norm Viols for Btwn 6 and 14")

dt[units_char %in% "Btwn 6 and 14", summary(n_vios_norm)]

ggplot(dt[units_char %in% "15 or more", ], aes(x=n_vios_norm)) + geom_histogram() + ggtitle("Norm Viols for 15 or more")
dt[units_char %in% "15 or more", summary(n_vios_norm)]
```

#### What is the 80th percentile?
Which properties are in the 75th percentile of this distribution?
```{r echo=FALSE}
small <- dt[units_char %in% "10 or less", ]
med <- dt[units_char %in% "Btwn 11 and 30", ]
large <- dt[units_char %in% "30 or more", ]
```

#### Small buildings
```{r echo=FALSE, warning=FALSE, message=FALSE}
plot(ecdf(small$n_vios_norm))
quantile(small$n_vios_norm, .80)
```

#### Medium buildings
```{r echo=FALSE, warning=FALSE, message=FALSE}
plot(ecdf(med$n_vios_norm))
quantile(med$n_vios_norm, .80)
```

#### Large buildings
```{r echo=FALSE, warning=FALSE, message=FALSE}
plot(ecdf(large$n_vios_norm))
quantile(large$n_vios_norm, .80)
```


#### Let's subset to the buildings that are beyond these thresholds (the 80th percentile)
```{r}
lg_80 <- quantile(large$n_vios_norm, .80)
med_80 <- quantile(med$n_vios_norm, .80)
small_80 <- quantile(small$n_vios_norm, .80)

lg_adds <- large[n_vios_norm > lg_80, unique(address)]
med_adds <- med[n_vios_norm > med_80, unique(address)]
sm_adds <- small[n_vios_norm > small_80, unique(address)]

all_adds <- c(lg_adds, med_adds, sm_adds)
worst <- bc_pluto[address %in% all_adds, ]
ggplot(worst, aes(x=n_vios)) + geom_histogram() + facet_wrap(~units_char)

# ggplot(worst, aes(x=total_units)) + geom_histogram()
# what is going on - why are we capturing so many 0-5 

worst[n_vios_norm < 1, unique(n_vios)]

```

#### Have any been through TPT or AEP?
```{r echo=FALSE, warning=FALSE, message=FALSE}
tpt[bbl %in% worst$bbl, ]
tpt_admin[BBL %in% worst$bbl, unique(bbl)]
aep[bbl %in% worst$bbl, unique(address)]
```


#### For these really bad buildings, let's look at lien data (not considering date of violation)
```{r echo=FALSE, warning=FALSE, message=FALSE}

lien_sale_lists <- fread("https://data.cityofnewyork.us/resource/9rz4-mjek.csv?$limit=99999")

lien_sale_lists[, block := str_pad(block, 5, "left", pad = 0)]
lien_sale_lists[, lot := str_pad(lot, 4, "left", pad = 0)]
lien_sale_lists[, bbl := paste(borough, block, lot, sep = "")]

# can we figiure out what we are missing 
# lets look at the distribution of liens 
liens_all[, bbl := as.character(bbl)]
liens_all[, tot_chg := as.numeric(`Total Charges`)]
liens_sub <- liens_all[tot_chg > 57595.24, ]

liens_amount <- merge(worst, liens_all, by = "bbl")

ggplot(liens_amount, aes(x=tot_chg)) + geom_histogram()
sub <- liens_amount[, .(tot_chg, n_vios_norm, bbl)]
sub <- unique(sub)
ggplot(sub, aes(x=n_vios_norm, y=tot_chg)) + geom_point()

#remove outliers 
sub <- sub[tot_chg < 5000000,]
ggplot(sub, aes(x=n_vios_norm, y=tot_chg)) + geom_point() + scale_y_continuous(labels = scales::dollar)

# let's check out that Davidson property from the city article 
liens_all[grep("2201 Davidson", address, ignore.case = TRUE), ]
worst[grep("2201 Davidson", address, ignore.case = TRUE), ]
```


#### Let's look at the distribution of b&c violations, value, liens for the TPT admin doc
```{r echo=FALSE, warning=FALSE, message=FALSE}
tpt_admin[,bc18 := `Open B+C Violations (2018)`]
tpt_admin[, bc18:=as.numeric(bc18)]
ggplot(tpt_admin, aes(x=bc18)) + geom_histogram()
plot(ecdf(tpt_admin$bc18))

# per dwelling unit 
tpt_admin[, units := as.numeric(`Dwelling Units`)]
tpt_admin[, bc18_unit := bc18/units]
plot(ecdf(tpt_admin$bc18_unit))
quantile(tpt_admin$bc18_unit, .80, na.rm = TRUE)

tpt_admin_sub <- tpt_admin[bc18_unit > 0, ]
quantile(tpt_admin_sub$bc18_unit, .80, na.rm = TRUE)
# ggplot(tpt_admin, aes())

# let's just look at the eligible buildings 
tpt_sub <- tpt_admin[`City Council vote` %in% "Approved", ]

# let's look at the distribution of liens and market values from the admin 
ggplot(tpt_sub, aes(x=units)) + geom_histogram()
tpt_sub[, mark_val := as.numeric(`Market Value (2018)`)]
ggplot(tpt_sub, aes(x=mark_val)) + geom_histogram() + scale_x_continuous(labels = scales::dollar)

tpt_sub[, open_vios := as.numeric(`Open B+C Violations (2018)`)]

ggplot(tpt_sub, aes(x=units, y=mark_val)) + geom_point()
ggplot(tpt_sub, aes(x=units, y=open_vios)) + geom_point()

```




