---
title: "Code Enforcement 11/15/22"
author: "Brook Frye"
date: "11/15/2022"
output: html_document
---


### Overall, how many buildings have been through these programs, 2017-present
-- ERP via open work orders and handyman work orders 
  -- OF  these, how many have gone through AEP (very few for buildings fixed internally)

-- How many HMCV violations across the city, which buildings have the most
-- Housing litigation repeats
-- Which buildings have gone thru multiple programs
---- is there any real reason why this would be?


####  Number of buildings that have gone through ERP via handyman work orders -- repairs carried out by agency staff
```{r echo=FALSE}
library(data.table)
library(ggplot2)
library(DT)
# carried out by agency staff
hwo <- fread("https://data.cityofnewyork.us/resource/sbnd-xujn.csv?$limit=999999")

# subset to 2017-present
hwo[, hwocreatedate:= as.Date(hwocreatedate)]
hwo[, year_create := year(hwocreatedate)]
hwo_sub <- hwo[year_create>=2017, ]
hwo_sub[, .N, by ="year_create"][order(year_create, decreasing = TRUE)]
# not useful to do by day
# hwo_sub[, charge_per_day := sum(chargeamount), by = "hwocreatedate"]
# hwo_sub[, n_per_year := .N, by = "hwocreatedate"]

hwo_sub[, n_per_year_boro := .N, by = .(boro, year_create)]
hwo_sub[, charge_per_year_boro:= sum(chargeamount), by = .(boro, year_create)]
hwo_sub[, AEP := ifelse(isaep=="AEP", 1, 0), by=.(boro, year_create)]
hwo_sub[, AEP:= sum(AEP), by = .(boro, year_create)]

boro_year <- hwo_sub[,.(Borough=boro, Year=as.factor(year_create), N=as.factor(n_per_year_boro), `Total Charge` = scales::dollar(charge_per_year_boro ), AEP)]
boro_year[, prop_aep := round(as.numeric(AEP)/as.numeric(N), 2)]

boro_year <- unique(boro_year)

# how many per year grouped by boro
ggplot(boro_year, aes(x=Year, y=N, fill=Borough)) + geom_col(position = "dodge") + theme_minimal() +  ggtitle("ERP Work Orders: Handled internally, Number of Buildings")

# prop AEP
ggplot(boro_year, aes(x=Year, y=prop_aep, fill=Borough)) + geom_col(position = "dodge") + theme_minimal() +  ggtitle("ERP Work Orders: Handled internally, Number of Buildings")

# how much $ per year
ggplot(boro_year, aes(x=Year, y=boro_year$`Total Charge`, fill=Borough)) +geom_col(position = "dodge") + theme_minimal() +  ggtitle("ERP Work Orders: Handled internally, Charges") + ylab("Total Charges")

DT::datatable(boro_year)


```



### ERP open market orders (not handled by agency staff)
```{r echo=FALSE}

omo <- fread("https://data.cityofnewyork.us/resource/mdbu-nrqn.csv?$limit=9999999")
# subset to 2017-present
omo[,omocreatedate:= as.Date(omocreatedate)]
omo[, year_create := year(omocreatedate)]
omo_sub <- omo[year_create>=2017, ]
omo_sub[, .N, by ="year_create"][order(year_create, decreasing = TRUE)]
omo_sub[, omo_award_tot := sum(omoawardamount), by = .(boro, year_create)]
omo_sub[, n_per_year_boro := .N, by = .(boro, year_create)]
omo_sub[, AEP := ifelse(isaep=="AEP", 1, 0), by=.(boro, year_create)]
omo_sub[, AEP:= sum(AEP), by = .(boro, year_create)]


boro_year_omo <- omo_sub[,.(Borough=boro, Year=as.factor(year_create), N=as.factor(n_per_year_boro), `Total Charge` = scales::dollar(omo_award_tot), AEP)]
boro_year_omo <- unique(boro_year_omo)
boro_year_omo[, prop_aep := round(as.numeric(AEP)/as.numeric(N), 2)]

# total number 
ggplot(boro_year_omo, aes(x=Year, y=N, fill=Borough)) + geom_col(position = "dodge") + theme_minimal() +  ggtitle("ERP Work Orders: Hired outside agency, Number of Buildings") 

# proportion that are AEP
ggplot(boro_year_omo, aes(x=Year, y=boro_year_omo$prop_aep, fill=Borough)) +geom_col(position = "dodge") + theme_minimal() +  ggtitle("ERP Work Orders: Handled externally, % AEP") + ylab("% AEP")

# how much $ per year total
ggplot(boro_year_omo, aes(x=Year, y=boro_year_omo$`Total Charge`, fill=Borough)) +geom_col(position = "dodge") + theme_minimal() +  ggtitle("ERP Work Orders: Handled internally, Charges") + ylab("Total Charges")

# how many completed?

DT::datatable(boro_year_omo)
```


### how many in total, any buildings that have gone through both?
```{r echo=FALSE}
hwo[, workorder := "hw"]
hwo[, descript := hwodescription]
omo[,workorder := "om"]
omo[, descript:=omodescription]


all_cases <- rbind(hwo, omo, fill=TRUE)
all_cases_sub <- all_cases[year_create>=2017,.(buildingid,descript, workorder, year_create)]

all_cases_sub <- unique(all_cases_sub)
both_gen <- all_cases_sub[, .(un_wo = unique(workorder)), by = .(buildingid)]
both_gen <- unique(both_gen)
mult_id <- both_gen[,.N, by = .(buildingid)][order(N, decreasing = TRUE)][N==2, .(buildingid)]

mults_gen <- all_cases_sub[buildingid %in% mult_id$buildingid, ]
mults_gen <- unique(mults_gen)

n_wo <- mults_gen[,.N, by="buildingid" ][order(N, decreasing = TRUE)]
ggplot(n_wo, aes(x=N)) + geom_histogram() + theme_bw()


# test
# all_cases_sub[buildingid %in% 165535, ]

both_year <- all_cases_sub[, unique(workorder), by = .(buildingid, year_create)]






# buildings that have been in both?
# buildings that have had ERPs multiple times


omo_sub[buildingid %in% hwo_sub$buildingid, .N, by = "buildingid"][order(N, decreasing = TRUE)]
```





```{r}

```

### Housing maintenance code violations 
-- How many for each type, each year by borough and council district
```{r echo=FALSE}

```




### Housing litigation data
```{r echo=FALSE}
# how many since 2017
hl <- fread("https://data.cityofnewyork.us/resource/59kj-x8nc.csv?$where=caseopendate>='2017-01-01'&$limit=999999999999")

hl[, year_open := year(as.Date(caseopendate))]
hl <- hl[!year_open %in% "2030", ]

# how many judgement
hl[, .N, by = c("casejudgement", "year_open", "casestatus")][order(year_open, decreasing = TRUE)]

# for the yes findings,  what is the nature of the complaint 

# for the no findings, what is the nature of the complaint

```



### heat sensor program
```{r echo=FALSE}

```

```{r echo=FALSE, include=FALSE, eval=FALSE}


# scratch 

## how many are in aep
omo_dt[, n_year := .N, by = "year_create"]

year_aep <- omo_dt[isaep %in% "AEP", .(.N, n_year), by = "year_create"][, .(year_create, prop_aep =N/n_year)]

# what is the prop of AEPs that are ERP across years
year_aep <- unique(year_aep)

# hwo_dt <- hwo_sub[,.(n_per_day, charge_per_day, year_create, hwocreatedate, boro, n_per_year_boro)]
# hwo_dt <- unique(hwo_dt)
# hwo_dt[, Year := as.factor(year_create)]
# hwo_dt[, day_of_year  := as.numeric(format(as.Date(hwocreatedate), "%j"))]




```

