---
title: "Code Enforcement Data Exploration"
author: "Brook Frye"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    theme: cosmo
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(ggplot2)
library(DT)
library(sf)
library(leaflet)
library(councildown)
library(dplyr)
```

#### ERP (2017-Present)
- [Repairs carried out by agency staff/internally, 2017 to present]
***
```{r echo=FALSE}


hwo <- fread("https://data.cityofnewyork.us/resource/sbnd-xujn.csv?$limit=999999")
pluto <- fread("~/Desktop/housing_builds/HB_TPT/pluto_22v3.csv")
cd_shp <- read_sf("~/Desktop/housing_builds/HB_TPT/data/input/nycc_shp")
cd_shp$council_district <- cd_shp$coun_dist

# how many buildings per council district
pluto_sub <- pluto[unitsres>1,.(n_bdgs_cd = .N), by =.(council)]
setnames(pluto_sub, "council", "council_district")

# subset to 2017-present
hwo[, hwocreatedate:= as.Date(hwocreatedate)]
hwo[, year_create := year(hwocreatedate)]
hwo_sub <- hwo[year_create>=2017, ]

# for jose
hwo_sub[,.(total_charges=sum(chargeamount)), by = "year_create"][order(year_create, decreasing = TRUE)]

# create total per day columns: N, charge
hwo_sub_plut <- merge(hwo_sub, pluto_sub)
hwo_sub_plut[, n_p_day := length(unique(hwocreatedate)), by = .(buildingid)]

hwo_sub_plut[, n_per_year_cd := sum(n_p_day), by = .(council_district, year_create)]
hwo_sub_plut[, charge_per_year_cd:= sum(chargeamount), by = .(council_district, year_create)]
hwo_sub_plut[, prop_n:= n_per_year_cd/n_bdgs_cd, by = .(council_district, year_create)]
hwo_sub_plut[, charge_p_bdg:= charge_per_year_cd/n_bdgs_cd, by=.(council_district, year_create)]

mapdt <-  unique(hwo_sub_plut[!is.na(council_district),.(council_district, prop_n = round(prop_n, 2), charge_p_bdg=round(charge_p_bdg, 2), total_cost = scales::dollar(charge_per_year_cd), Year=year_create, `Total Number` = n_per_year_cd)]) 

map_sf <- mapdt %>% 
  left_join(cd_shp, by = "council_district") %>% 
  st_as_sf() %>% 
  st_transform(crs='+proj=longlat +datum=WGS84')

setDT(map_sf); map_sf[, Year := as.character(Year)]
map_list <- split(map_sf, map_sf$Year) 
map_list2 <- lapply(map_list,st_as_sf)

```

- [Repairs carried out by Handyman Work Orders]
```{r echo=FALSE}
pal <- colorNumeric("viridis", map_sf$prop_n)
leaflet() %>% 
  addCouncilStyle() %>% 
  addPolygons(data = map_list2[[1]],
              fillColor = ~pal(prop_n), 
              color = ~pal(prop_n),
              weight = 1, 
              label = ~paste("Raw Total:", `Total Number`), 
              group = "2017",
              opacity = 1, 
              fillOpacity = .2) %>%
   addPolygons(data = map_list2[[2]],
              fillColor = ~pal(prop_n), 
              color = ~pal(prop_n),
              weight = 1, 
              label = ~paste("Raw Total:", `Total Number`), 
              group = "2018",
              opacity = 1, 
              fillOpacity = .2) %>%
   addPolygons(data = map_list2[[3]],
              fillColor = ~pal(prop_n), 
              color = ~pal(prop_n),
              weight = 1, 
              label = ~paste("Raw Total:", `Total Number`), 
              group = "2019",
              opacity = 1, 
              fillOpacity = .2) %>%
   addPolygons(data = map_list2[[4]],
              fillColor = ~pal(prop_n), 
              color = ~pal(prop_n),
              weight = 1, 
              label = ~paste("Raw Total:", `Total Number`), 
              group = "2020",
              opacity = 1, 
              fillOpacity = .2) %>%
   addPolygons(data = map_list2[[5]],
              fillColor = ~pal(prop_n), 
              color = ~pal(prop_n),
              weight = 1, 
              label = ~paste("Raw Total:", `Total Number`), 
              group = "2021",
              opacity = 1, 
              fillOpacity = .2) %>%
    addPolygons(data = map_list2[[6]],
              fillColor = ~pal(prop_n), 
              color = ~pal(prop_n),
              weight = 1, 
              label = ~paste("Raw Total:", `Total Number`), 
              group = "2022",
              opacity = 1, 
              fillOpacity = .2) %>%
    addLegend(position = "bottomleft", pal = pal, values = map_sf$prop_n, title = "# HWO/<br>Total Bdgs") %>% 
    addLayersControl(
    baseGroups = c("2017", "2018","2019", "2020", "2021", "2022"),
    options = layersControlOptions(collapsed = FALSE))
  
```

- [Cost per building via handyman work orders]
```{r echo=FALSE}
pal <- colorNumeric("viridis", map_sf$charge_p_bdg)

l <- leaflet() %>% addCouncilStyle()

names(map_list2) %>%
  purrr::walk(function(df) {
    l <<- l %>%
      addPolygons(data=map_list2[[df]],
              fillColor = ~pal(charge_p_bdg), 
              color = ~pal(charge_p_bdg),
              weight = 1, 
              label = ~paste("Total Cost:", `total_cost`), 
              group = df,
              opacity = 1,
              fillOpacity = .3)})
l %>% 
    addLegend(position = "bottomleft", pal = pal, values = map_sf$charge_p_bdg, title = "HWO Cost Adjusted <br> (Total Cost/N Buildings)") %>% 
    addLayersControl(
    baseGroups = c("2017", "2018","2019", "2020", "2021", "2022"),
    options = layersControlOptions(collapsed = FALSE))
  
  
```


- [Repairs carried out by open market orders]
***
```{r echo=FALSE}
omo <- fread("https://data.cityofnewyork.us/resource/mdbu-nrqn.csv?$limit=9999999")
# subset to 2017-present
omo[,omocreatedate:= as.Date(omocreatedate)]
omo[, year_create := year(omocreatedate)]
omo_sub <- omo[year_create>=2017, ]

omo_sub_plut <- merge(omo_sub, pluto_sub)

# totals by bdg 
omo_sub_plut[, n_bdg := length(unique(omocreatedate)), by = .(buildingid)]
omo_sub_plut[, total_charg_bdg := sum(omoawardamount), by = .(buildingid)]

# total OMOs by year, year and council distr
omo_sub_plut[, n_p_bdg:= length(unique(omocreatedate)), by = .(buildingid, year_create)]
omo_sub_plut[,  n_per_year_cd := sum(n_p_bdg), by = .(buildingid, council_district, year_create)]

# normalize
omo_sub_plut[, award_per_year_cd:= sum(omoawardamount), by = .(council_district, year_create)]
omo_sub_plut[, prop_n:= n_per_year_cd/n_bdgs_cd, by = .(council_district, year_create)]
omo_sub_plut[, award_p_bdg:= award_per_year_cd/n_bdgs_cd, by=.(council_district, year_create)]

mapdt <-  unique(omo_sub_plut[!is.na(council_district),.(council_district, prop_n = round(prop_n, 2), `Total Award` = scales::dollar(award_p_bdg), Year=year_create, `Total Number` = n_per_year_cd)]) 

mapdt <- unique(mapdt)


```

##### OMO number per building summary
```{r}
sum_dt <- omo_sub_plut[, .(n_bdg, total_charg_bdg)]
sum_dt <- unique(sum_dt)

summary(sum_dt$n_bdg)
```


##### OMO award per building summary
```{r}
summary(omo_sub_plut$award_p_bdg)
```

```{r}
map_sf <- mapdt %>% 
  left_join(cd_shp, by = "council_district") %>% 
  st_as_sf() %>% 
  st_transform(crs='+proj=longlat +datum=WGS84')

setDT(map_sf); map_sf[, Year := as.character(Year)]
map_list <- split(map_sf, map_sf$Year) 
map_list2 <- lapply(map_list,st_as_sf)
```


```{r}
pal <- colorNumeric("viridis", map_sf$prop_n)

l <- leaflet() %>% addCouncilStyle()

names(map_list2) %>%
  purrr::walk(function(df) {
    l <<- l %>%
      addPolygons(data=map_list2[[df]],
              fillColor = ~pal(prop_n), 
              color = ~pal(prop_n),
              weight = 1, 
              # label = ~paste("Total Number of OMO", `Total Num`), 
              group = df,
              opacity = 1,
              fillOpacity = .3)})
l %>% 
    addLegend(position = "bottomleft", pal = pal, values = map_sf$prop_n, title = "Proportion of Bdgs with OMOs") %>% 
    addLayersControl(
    baseGroups = c("2017", "2018","2019", "2020", "2021", "2022"),
    options = layersControlOptions(collapsed = FALSE))
```


```{r}
pal <- colorNumeric("viridis", map_sf$`Total Award`)

l <- leaflet() %>% addCouncilStyle()

names(map_list2) %>%
  purrr::walk(function(df) {
    l <<- l %>%
      addPolygons(data=map_list2[[df]],
              fillColor = ~pal(`Award per Bdg`), 
              color = ~pal(`Award per Bdg`),
              weight = 1, 
              label = ~paste("Total Award:", `Total Award`), 
              group = df,
              opacity = 1,
              fillOpacity = .3)})
l %>% 
    addLegend(position = "bottomleft", pal = pal, values = map_sf$`Award per Bdg`, title = "Award per ") %>% 
    addLayersControl(
    baseGroups = c("2017", "2018","2019", "2020", "2021", "2022"),
    options = layersControlOptions(collapsed = FALSE))
  

```


```{r echo=FALSE}
hwo[, workorder := "hw"]
hwo[, descript := hwodescription]
omo[,workorder := "om"]
omo[, descript:= omodescription]


all_cases <- rbind(hwo, omo, fill=TRUE)
all_cases_rec <- all_cases[year_create>=2017,] # make sure not double counting
all_cases_sub <- all_cases_rec[,.(buildingid, descript, workorder, year_create)]

all_cases_sub <- unique(all_cases_sub)
both_gen <- all_cases_sub[, .(un_wo = unique(workorder)), by = .(buildingid)]
both_gen <- unique(both_gen)
mult_id <- both_gen[,.N, by = .(buildingid)][order(N, decreasing = TRUE)][N==2, .(buildingid)]

mults_gen <- all_cases_sub[buildingid %in% mult_id$buildingid, ]
mults_gen <- unique(mults_gen)
n_wo <- mults_gen[,.N, by="buildingid"]


```

#### Buildings that have been in ERP multiple times (more than once)
- [consider multiple visits in a day to one building one visit]
```{r echo=FALSE, eval=FALSE}

```


#### AEP
- How many buildings have been through AEP more than once?
- 386 buildings go through AEP more than once.
```{r echo=FALSE}
aep <- fread("https://data.cityofnewyork.us/resource/hcir-3275.csv?$limit=999999")
aep[, aep_start_date:= as.Date(aep_start_date)]
aep[, aep_discharge_date := as.Date(discharge_date)]

aep[building_id %in% mults_gen$buildingid, .N]
aep[, Duration:= as.numeric(aep_discharge_date-aep_start_date)]
aep[, .N, by ="building_id"][order(N, decreasing = TRUE)]

# how long
```

#### Housing maintenance code violations 
What is the distribution?

```{r echo=FALSE}
#hmv <- fread("https://data.cityofnewyork.us/resource/wvxf-dwi5.csv?$limit=9999999999999")

hmv <- fread("~/Desktop/housing_builds/HB_TPT/hmv_sub.csv")
hmv[, novissueddate := as.Date(novissueddate)]
hmv[, currentstatusdate := as.Date(currentstatusdate)]
hmv_sub <- hmv[novissueddate>=as.Date("2017-01-01") & !currentstatus %in% "VIOLATION DISMISSED", ]

hmv_sub[boroid %in% 4, Borough := "Queens"]
hmv_sub[boroid %in% 3, Borough := "Brooklyn"]
hmv_sub[boroid %in% 1, Borough := "Manhattan"]
hmv_sub[boroid %in% 2,Borough := "Bronx"]
hmv_sub[boroid %in% 5,Borough := "Staten Island"]

# distribution of number of violations by building 


# write.csv(hmv_sub, "hmv_sub.csv")

```


#### Housing litigation data
- [Broken down by 7A and CONH, tenant driven, HPD driven]
- There are many blanks in the respondent column
```{r echo=FALSE}
# how many since 2017
hl <- fread("https://data.cityofnewyork.us/resource/59kj-x8nc.csv?$where=caseopendate>='2017-01-01'&$limit=999999999999")
hl[, year_open := year(as.Date(caseopendate))]
hl <- hl[!year_open %in% "2030", ]

# merge with violations - add date
hmv_hl <- hmv_sub[buildingid %in% hl$buildingid, .(violationid, buildingid, violationstatus, currentstatusdate, currentstatus, class, latitude, longitude)]

hl_map <- hl[buildingid %in% hmv_sub$buildingid, .(respondent, Location=paste(housenumber, streetname, nta), buildingid)]

hmv_hl <- unique(hmv_hl)
hmv_hl[,n_per_bdg:=.N, by = .(buildingid)]
hmv_hl[,n_per_bdg_class:=.N, by = .(buildingid, class)]
summary(hmv_hl$n_per_bdg)
hist_dt <- hmv_hl[, .(buildingid, n_per_bdg, class)]
hist_dt <- unique(hist_dt)

```

#### Did 7A impact the number of complaints or violations?
```{r echo=TRUE}
# use https://data.cityofnewyork.us/Housing-Development/Housing-Maintenance-Code-Complaints/uwyv-629c


```

#### Underlying Conditions
```{r echo=FALSE}

```

#### Heat Sensor 
```{r echo=FALSE}

```


#### [Who are the owners and how many buildings do they own] (https://data.cityofnewyork.us/City-Government/Property-Valuation-and-Assessment-Data/yjxr-fw8i/data)

```{r echo=FALSE}
pv <- fread("https://data.cityofnewyork.us/resource/8y4t-faws.csv?$limit=99999999") 
test <- aep[building_id %in% mult_aep$building_id, .(as.character(bbl))]

pv[parid %in% test$V1,.N, by = .(owner) ]

pv[owner %in% "MERCY HOLDING LLC", ]
# pv[,.N, by= "owner"][order(N,decreasing = TRUE)][1:60]
hl[as.character(bbl) %in% test$V1, ]


### for james just fix scrape
# resps <- hl[!respondent %in% "",.(respondent)]
# resps2 <- strsplit(resps$respondent, ",")
# resps3 <- lapply(resps2, function(x) gsub("ET AL", "", x))
# resps4 <- lapply(resps3, function (x) trimws(x, which = "both"))
# write.csv(unlist(resps4), "justfixscrape_hl.csv")
```

#### Property Balance Data - can we estimate recovery here?
```{r echo=FALSE}

```

